On Secure Delegation of SampBQP with a Classical Client

### 2020-02-09 bqp.tex
Make another editorial pass at BQP section

\Ethan{TODO Read other papers and see if I can copy their tones and phrasing}

\Ethan{Note to self: If the original is wordy, just keep it the way it is. Don't try to simplify existing dfns.}

@@

\Ethan{See https://www.iis.sinica.edu.tw/~kmchung/download/ConstCZK.pdf for conventions. Mal. parties have stars, protos use Pi. Stuff like $r(P(w), V )(1n ,(M, x, t))$ }

\Ethan{More notation, fix interfaces}

\Ethan{Fix up to proto 3 and proofs}

@@

We start with a high-level description of the $\QPIP_1$ scheme from \cite{mahadev_delegation}, which is in turn taken from \cite{mf16}.

This is a one-message $\QPIP_1$ protocol with only $X$ and $Z$ measurement for deciding a $\BQP$ language $L$.
Roughly, on input $x\in\set{0,1}^n$, the prover sends a $m$-qubit certificate state $\rho$ to the verifier qubit-by-qubit.
The verifier samples a product measurement $\Lambda$ of $X$ and $Z$s according to certain distribution to apply to $\rho$
The verifier then, using the measurement results, decides whether to accept or reject.

@@

We compile this protocol using Mahadev's $\QHE$ from \cite{mahadev_qfhe} to obtain a blind 1-message $\QPIP_1$ protocol for $\BQP$, again with only $X$ and $Z$ measurements.
The high level idea is to run $\PiMF$ under $\mathsf{QHE}$.
Namely, the verifier encrypts its original input $x$ and sends $y=\mathsf{QHE.Enc}(x)$ to the prover.
The prover then homomorphically evaluate $\cF$ on $y$ to produce $\sigma$ which is a ciphertext corresponding to $\rho$, and sends $\sigma$ to the verifier.

Now the verifier needs to obtain the measurement outcome $w$ from the encrypted state $\sigma$ using qubit-by-qubit $X$ and $Z$ measurements.
This may not be possible in general, but we observe that $\mathsf{QHE}$ allows this. 
Its ciphertexts consists of a Pauli one-time-padded plaintext and classically encrypted Pauli keys.
Pauli one-time-pads commute with $X$ and $Z$ measurements, so the verifier can measure the one-time-padded state as usual then correct the measurement results using the Pauli keys.
We state this observation as the following theorem:

@@

	There exists efficient classical poly-time algorithms $\cM_\QHE$ and $\widehat{\mathsf{QHE.Dec}}$ s.t.
	for all $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_n$ where each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement:
	\Ethan{How to specify the existence of $sk$?}
	$$\cM_\QHE(\Lambda)=\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$$
	where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and
	$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
\end{thm}
\begin{prf}
	This is a proof by construction.
	We require $\Lambda'$ and $\widehat{\mathsf{QHE.Dec}}$ such that $\forall\sigma=(X^xZ^z\rho Z^zX^x, c_{x,z})$,
	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'(\sigma)$$
	Clearly,
	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\Lambda(\rho)$$

@@

Now we state our construction to compile $\PiMF$ using $\mathsf{QHE}$:

@@

As we will prove, $\Piblind$ is a $\QPIP_1$, constant round, and blind protocol for $\BQP$ with negligible completeness and soundness.

@@

Finally, we prove Thm 3.1 by applying Mahadev's measurement protocol~\cite{mahadev_delegation} to Protocol 3 to compile it into a $\QPIP_0$ protocol $(P', V')$ \Ethan{fix name}.
Note that Mahadev's measurement protocol can compile any $\QPIP_1$ protocol with X, Z measurement and negligible soundness to a $\QPIP_0$ protocol, and Protocol 3 is a $\QPIP_1$ protocol with X, Z measurement and negligible soundness.
Thus the resulting protocol $(P', V')$ \Ethan{name?} is a O(1)-round $\QPIP_0$ protocol with soundness error $\frac{3}{4} + \negl(n)$

We give a high-level overview of the compiliation results.

@@

Let $f\in\FBQP$.
For any input $x\in\set{0, 1}^*$, define $f_i(x)$ to be the $i$-th bit of $f(x)$.
For $i\in\bbN, b\in\set{0,1}$, define the language $L_{i, b}=\set{x:f_i(x)=b}$.
Define $\cL$ to be the collection of these languages: $\cL = \set{L_{i, b}: i\in[m], b\in\set{0, 1}}$.

\begin{protocol}{Blind and verifiable $\QPIP_0$ delegation for $\FBQP$}
	\label{proto:QPIP0FBQP}
	Input: $x\in\set{0, 1}^n$

	Suppose without loss of generality that the verifier knows $f(x)$ is of length $m=\poly(n)$ \Ethan{Seems like a strong assumption; maybe need to explain how?}
	\begin{enumerate}
		\item Run $\Pibzrep$ for all $L\in\cL$ in parallel using input $x$. The verifier gets outputs $v_{i, b}\in\set{Acc, Rej}$.
		\item If $\exists i$ s.t. $v_{i,0}=v_{i,1}$, reject.
		\item Otherwise, define $y_i = b$ where $v_{i, b}=Acc$. This gives $y\in\set{0,1}^m$
		\item Verifier outputs $y$
	\end{enumerate}
\end{protocol}

\begin{theorem}
	\Cref{proto:QPIP0FBQP} has negligible completeness and soundness, and is blind.
\end{theorem}
\begin{prf}
	Completeness is follows by inspection.
	Blindness follows because the executions of \cref{proto:repQPIP0BQP} are blind.

	Based on the soundness of \cref{proto:BlindBQP}, $v_{i, b}=Acc$ implies that $x\in L_{i, b}\Rightarrow f_i(x)=b$ with overwhelming probability.
	In other words, $y_i$ is correct with probability $1-\varepsilon_i$ where $\varepsilon_i=\negl(n)$.

>>>>

@@

@@

We start with a high-level description of the $\QPIP_1$ scheme $\PiMF$ from \cite{mahadev_delegation}, which is in turn taken from \cite{mf16}.

This is a one-message $\QPIP_1$ protocol with only $X$ and $Z$ measurement for deciding a $\BQP$ language $L$.
Roughly, on input $x\in\set{0,1}^n$, the prover sends a $m$-qubit certificate state $\rho$ to the verifier qubit-by-qubit.
The verifier samples a product measurement $\Lambda$ of $X$ and $Z$s according to a certain distribution, and applies it to $\rho$.
The verifier then, using the measurement results, decides whether to accept or reject.

@@

We compile $\PiMF$ using Mahadev's $\QHE$ from \cite{mahadev_qfhe} to obtain a blind 1-message $\QPIP_1$ protocol $\Piblind$ for $\BQP$, again with only $X$ and $Z$ measurements.
The high level idea is to run $\PiMF$ under $\mathsf{QHE}$.
Namely, the verifier encrypts its original input $x$ and sends $y=\mathsf{QHE.Enc}(x)$ to the prover.
The prover then homomorphically evaluates $\cF$ on $y$ to produce $\sigma$ and sends it to the verifier.

Now the verifier needs to obtain the measurement outcome $w$ from the encrypted state $\sigma$ using qubit-by-qubit $X$ and $Z$ measurements.
This may not be possible in general, but we observe that $\mathsf{QHE}$ allows this. 
Its ciphertexts consists of a Pauli one-time-padded plaintext and classically encrypted Pauli keys.
Pauli one-time-pads commute with $X$ and $Z$ measurements, so the verifier can measure the one-time-padded state as usual, then correct the measurement results using the Pauli keys.
Now we state and prove this observation in more precise terms.

@@

	There exists efficient classical poly-time algorithms $\cM_\QHE$ and $\widehat{\mathsf{QHE.Dec}}$ s.t.
	for all $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_n$ where each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement:
	$$\cM_\QHE(\Lambda)=\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$$
	where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and
	$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
\end{thm}
\begin{prf}
	This is a proof by construction.
	We require $\Lambda'$ and $\widehat{\mathsf{QHE.Dec}}$ such that $\forall\sigma=(X^xZ^z\rho Z^zX^x, c_{x,z})$,
	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'(\sigma)$$
	Clearly,
	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\Lambda(\rho)$$

@@

Now we state our results of compiling $\PiMF$ using $\mathsf{QHE}$:

@@

@@

Finally, we prove \cref{thm:QPIP0BQP}.
We use Mahadev's measurement protocol from \cite{mahadev_delegation} which can compile any $\QPIP_1$ protocol with X, Z measurement and negligible soundness to a $\QPIP_0$ protocol.
The resulting protocol $\Pibz$ is a constant-round $\QPIP_0$ protocol with soundness error $\frac{3}{4} + \negl(n)$ and negligible completeness.

In order to prove blindness, we give a high-level overview of the compiliation results.
\Ethan{Need to discuss about this}

@@

Let $f\in\FBQP$.
For any input $x\in\set{0, 1}^*$, define $f_i(x)$ to be the $i$-th bit of $f(x)$.
For $i\in\bbN, b\in\set{0,1}$, define the language $L_{i, b}=\set{x:f_i(x)=b}$.
Furthermore, define $\cL$ to be the collection of these languages: $\cL = \set{L_{i, b}: i\in[m], b\in\set{0, 1}}$.

\begin{protocol}{Blind and verifiable $\QPIP_0$ protocol $\Pi_{\FBQP}$ for $\FBQP$ language $L$}
	\label{proto:QPIP0FBQP}
	Input: $x\in\set{0, 1}^n$

	Suppose without loss of generality that the verifier knows $f(x)$ is of length $m=\poly(n)$ \Ethan{Seems like a strong assumption; maybe need to explain how?}
	\begin{enumerate}
		\item Run $\Pibzrep$ for all $L\in\cL$ in parallel using input $x$.
		\item The verifier gets outputs $v_{i, b}\in\set{acc, rej}$.
			If $\exists i$ s.t. $v_{i,0}=v_{i,1}$, reject.
			Otherwise, define $y_i = b$ where $v_{i, b}=acc$. This gives $y\in\set{0,1}^m$.
			The verifier accepts and outputs $y$.
	\end{enumerate}
\end{protocol}

\begin{theorem}
	$\Pi_{\FBQP}$ has negligible completeness and soundness, and is blind.
\end{theorem}
\begin{prf}
	Completeness is follows by inspection.
	Blindness follows because the executions of \cref{proto:repQPIP0BQP} are blind.

	By the soundness of $\Pibzrep$, $v_{i, b}=acc$ implies that $x\in L_{i, b}\Rightarrow f_i(x)=b$ with overwhelming probability.
	In other words, $y_i$ is correct with probability $1-\varepsilon_i$ where $\varepsilon_i=\negl(n)$.
